# Multiple Regression

## Setup

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(broom)
library(modelsummary)

df <- read_csv("health.csv")
```

## Exploring the Data

```{r}
glimpse(df)
summary(df)
```

```{r}
ggplot(df, aes(x = faminc, y = bwght, color = cigs)) +
  geom_point()
```

```{r}
ggplot(df, aes(x = cigs, y = bwght, color = faminc)) +
  geom_point()
```

## Model 1: Full Model

```{r}
mod1 <- lm(bwght ~ ., data = df)
tidy(mod1)
glance(mod1)
```

Family income has a statistically significant but very small positive impact on birth weight. Cigarettes smoked has a statistically significant negative impact on birth weight.

## Model 2: Family Income Only

```{r}
mod2 <- lm(bwght ~ faminc, data = df)
tidy(mod2)
glance(mod2)
```

The significance of family income increases when it is the sole predictor, but the overall model fit decreases.

## Model 3: Cigarettes Only

```{r}
mod3 <- lm(bwght ~ cigs, data = df)
tidy(mod3)
glance(mod3)
```

## Model Comparison

```{r}
models <- list(
  "Model 1" = mod1,
  "Model 2" = mod2,
  "Model 3" = mod3
)

modelsummary(models)
```

```{r}
model_comparison <- bind_rows(
  glance(mod1) |> mutate(model = "Model 1"),
  glance(mod2) |> mutate(model = "Model 2"),
  glance(mod3) |> mutate(model = "Model 3")
) |>
  select(model, r.squared, adj.r.squared, sigma, AIC, BIC, p.value)

model_comparison
```
