# Multiple Regression — Solutions

## Setup

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(broom)
library(modelsummary)
```

## Exercise 4.1

The file `health.xls` contains data for birth_weight, cig, and fam_inc.

**(a) Regression with both variables**

```{r}

```

**(b) Regression with fam_inc only**

```{r}

```

**(c) Regression with cig only**

```{r}

```

**(d) Model comparison table**

```{r}

```

**(e) Wald test: effect of cig is two times greater than fam_inc**

```{r}

```

## Exercise 4.2

Determinants of log(wage): educ, exper, tenure.

**(a) Full model and results**

```{r}

```

**(b) Wald test: exper same effect as educ**

```{r}

```

**(c) Redundant variable test for exper**

```{r}

```

**(d) Omitted variable test for tenure**

```{r}

```

## Exercise 4.3

Aggregate demand for money: $\ln(M/P)_t = \alpha + \beta \ln(Y_t) + \gamma R_t + u_t$

**(a) Theory and interpretation**

<!-- Write your discussion here -->

**(b) Tests of significance**

```{r}

```

## Exercise 4.4

Cobb–Douglas production function and test for constant returns to scale.

```{r}

```

## Exercise 4.5

Mankiw, Romer and Weil (1992) growth regressions.

**(a) Create data frame**

```{r}

```

**(b) Load data**

```{r}

```

**(c) Summary statistics by sub-sample**

```{r}

```

**(d) Variable transformations**

```{r}

```

**(e) Reproduce TABLE I: Textbook Solow Model**

```{r}

```

**(f) Compare results with MRW**

```{r}

```

**(g) Test restriction: coefficient of ln(pop) = −ln(iy)**

```{r}

```

**(h) Reproduce TABLE II: Augmented Solow Model**

```{r}

```

**(i) Latest Penn World Table data (Advanced)**

```{r}

```
