# Multicollinearity — Solutions

## Setup

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(broom)
library(modelsummary)
library(car)
```

## Exercise 5.1

**(a) Full model**

```{r}

```

**(b) Correlation matrix**

```{r}

```

**(c) Regression: IMP on GDP only**

```{r}

```

**(d) Regression: IMP on CPI only**

```{r}

```

**(e) Auxiliary regression: GDP on CPI**

```{r}

```

**(f) Conclusions on multicollinearity**

<!-- Write your discussion here -->

## Exercise 5.2

**(a) Repeat with quarterly data**

```{r}

```

**(b) Do results change?**

<!-- Write your discussion here -->

## Exercise 5.3

**(a) Model with additional variable R2**

```{r}

```

**(b) Expectation of multicollinearity**

<!-- Write your discussion here -->

**(c) Correlation matrix**

```{r}

```

**(d) Auxiliary regressions and VIF**

```{r}

```

## Exercise 5.4

**(a) Log-linear demand model for new cars**

```{r}

```

**(b) Expectation of multicollinearity**

<!-- Write your discussion here -->

**(c) Detection of multicollinearity**

```{r}

```

**(d) Revised model avoiding multicollinearity**

```{r}

```

## Exercise 5.5

**(a) Can we estimate the model?**

```{r}

```

**(b) Reparameterisation**

```{r}

```

## Exercise 5.6

**(a) Regression of occup on all explanatory variables**

```{r}

```

**(b) Detection of collinearity**

```{r}

```
