# Heteroskedasticity — Solutions

## Setup

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(broom)
library(modelsummary)
library(lmtest)
library(sandwich)
```

## Exercise 6.1

**(a) Estimate the model**

```{r}

```

**(b) White test**

```{r}

```

**(c) Goldfeld–Quandt test**

```{r}

```

**(d) GLS with Var(u) = σ²·sqfeet**

```{r}

```

**(e) GLS with Var(u) = σ²·sqfeet²**

```{r}

```

**(f) Re-test for heteroskedasticity after correction**

```{r}

```

## Exercise 6.2

**(a) Estimate effect of size on profit/sales ratio**

```{r}

```

**(b) Tests for heteroskedasticity**

```{r}

```

**(c) White's corrected standard errors**

```{r}

```

**(d) Confidence intervals comparison**

```{r}

```

## Exercise 6.3

**(a) Estimate budget model**

```{r}

```

**(b) Heteroskedasticity tests**

```{r}

```

## Exercise 6.4

**(a) Check for heteroskedasticity**

```{r}

```

**(b) Variance comparison: men vs women**

```{r}

```

**(c) Re-estimate correcting for heteroskedasticity**

```{r}

```

## Exercise 6.5

**(a) Check for heteroskedasticity**

```{r}

```

**(b) Re-estimate with log(price) and re-test**

```{r}

```

**(c) Discussion on transformation and heteroskedasticity**

<!-- Write your discussion here -->

## Exercise 6.6

**(a) Estimate Y = a + bX + u**

```{r}

```

**(b) Check for heteroskedasticity**

```{r}

```

**(c) Re-estimate with transformed variables**

```{r}

```
