# Misspecification — Solutions

## Setup

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(broom)
library(modelsummary)
library(lmtest)
```

## Exercise 8.1

**(a) Summary statistics**

```{r}

```

**(b) Linear model: wage = f(IQ)**

```{r}

```

**(c) Log-linear model: log(wage) = f(IQ)**

```{r}

```

**(d) Box–Cox transformation**

```{r}

```

## Exercise 8.2

**(a) Estimate cubic cost function**

```{r}

```

**(b) Test: cost function is second degree only**

```{r}

```

**(c) Test: cost function is linear**

```{r}

```

**(d) Plot marginal cost function**

```{r}

```

## Exercise 8.3

**(a) Estimate Cobb–Douglas production function**

```{r}

```

**(b) Test significance of β1, β2 and overall model**

```{r}

```

**(c) Test constant returns to scale**

```{r}

```

**(d) Calculate APL and MPL**

```{r}

```

**(e) Ramsey RESET test (omitting X2)**

```{r}

```

## Exercise 8.4

**(a) Linear model**

```{r}

```

**(b) Log-linear model**

```{r}

```

**(c) Linear-log model**

```{r}

```

**(d) Double-log model**

```{r}

```

**(e) Compare linear vs double-log**

```{r}

```
