# Dummy Variables — Solutions

## Setup

```{r}
#| message: false
#| warning: false
library(tidyverse)
library(broom)
library(modelsummary)
```

## Exercise 9.1

**(a) Simple model: log(wage) on black**

```{r}

```

**(b) Extended model with educ, exper, tenure**

```{r}

```

**(c) Add IQ and KWW**

```{r}

```

**(d) Add married, south, urban dummies**

```{r}

```

**(e) Predicted wage for specific individual**

```{r}

```

**(f) Compare to non-Black, north, urban individual**

```{r}

```

## Exercise 9.2

**(a) Estimate log(bwght) model**

```{r}

```

**(b) Interpret coefficient of cigs (effect of one pack)**

```{r}

```

**(c) White vs non-White difference**

```{r}

```

**(d) Male vs female difference**

```{r}

```

**(e) Add father's and mother's education**

```{r}

```

## Exercise 9.3

**(a) Do males sleep more than females?**

```{r}

```

**(b) Add more explanatory variables for sleep**

```{r}

```

**(c) Do males earn higher wages?**

```{r}

```

**(d) Add more explanatory variables for wages**

```{r}

```

**(e) Black ethnic minority analysis**

```{r}

```
